---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# biathlonResults

<!-- badges: start -->
<!-- badges: end -->

biathlonResults is an inofficial wrapper around the API provided by [biathlonresults.com](https://biathlonresults.com/). The API is free and public, but undocumented. I drew on [this](https://github.com/prtkv/biathlonresults/blob/master/biathlonresults/api.py) implementation in python.

The package covers most of the API's functions and follows a [tidy-data](https://r4ds.had.co.nz/tidy-data.html) logic in the returned output (...well, mostly).


## Installation

You can install the development version of biathlonResults from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thieled/biathlonResults")
```

## Example

Here are a few examples how to use it. To get a list of all cups this season, call:

```{r example}
library(biathlonResults)
library(dplyr)
get_cups("2223") %>% select(CupId, Description, Level) %>% head(3)
```
Now, lets get the current (Season 22/23) Women's World Cup:
```{r}
get_cup_results("BT2223SWRLCP__SWTS") %>% select(Rank, IBUId, Name) %>% head(3)
```

Let's get Tandrevold's complete race result record and her skiiing and shooting stats of the past 4 seasons:
```{r}
get_results("BTNOR22309199601") %>% head(3) %>% select(RaceId, Comp, Place, Rank, Pen, Shootings)

get_stats("BTNOR22309199601")  %>% select(FullName, starts_with("Stat"))
```
Of course, we can also get the results of a specific race:
```{r}
get_race_results("BT2223SWRLCP02SMPU") %>% select(Comp.Description, Event.Organizer,
                                                  ShortName, Rank, TotalTime, Behind, Shootings) %>% head()
```

Have fun!
